Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-08 paper/paper.tex
Add more details on controller implementation

\usepackage{caption}
\usepackage{subfig}
\usepackage{todonotes}
\usepackage[hidelinks]{hyperref}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{microtype}

@@

We currently deal with a read-only workload where the distribution of data is known by all nodes.
Each node is able to calculate the fraction of query results it will return.
A node can signal the expected fraction of the results for a query it will return by setting bits within the packet header.
When a new flow is issued for query processing, the controller can inspect these bits and assign an appropriate priority to each flow.
The controller is similar to a simple L2 learning switch.
However, we configure several queues for each switch port which allow us to provide bandwidth reservations to support variation in expected traffic volume.

@@

We run all our experiments on a simulated network on a single machine using Mininet~\cite{Lantz2010}.
We use Open vSwitch~\cite{Pfaff2009} as our switch which supports queues with varying bandwidth guarantees.
Our controller uses the POX~\cite{Gude2008} platform and OpenFlow~\cite{McKeown2008} 1.0.

>>>>

\usepackage{caption}
\usepackage{subfig}
\usepackage{todonotes}
\usepackage[hidelinks]{hyperref}
\usepackage{fixltx2e}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage{listings}

@@

We currently deal with a read-only workload where the distribution of data is known by all nodes.
Each node is able to calculate the fraction of query results it will return.
A node can signal the expected fraction of the results for a query it will return by setting bits within the packet header.
When a new flow is issued for query processing, the controller can inspect these bits and assign an appropriate priority to each flow.
The controller is similar to a simple L2 learning switch.
However, we configure several queues for each switch port which allow us to provide bandwidth reservations to support variation in expected traffic volume.
Once we have learned the port mapping, we simply install a rule that also matches on the DSCP bits and assigns the packet to an appropriate queue as in Figure~\ref{fig:scheduling}, which shows some sample code from our controller.

\begin{figure*}
    \begin{lstlisting}[language=Python]
        # Only perform queue assignment for IP packets
        if(packet.type == 0x0800):
          # Extract the DSCP bits from the ToS (ignoring ECN)
          queue_num = (packet.payload.tos >> 2)

          # Send the packet to the appropriate queue
          msg.actions.append(of.ofp_action_enqueue(port=port, queue_id=queue_num))
        else:
          # Send all non-IP packets to a queue with higher priority
          msg.actions.append(of.ofp_action_enqueue(port=port, queue_id=0))
    \end{lstlisting}
    \caption{Simple flow scheduling to queues}\label{fig:scheduling}
\end{figure*}

@@

We run all our experiments on a simulated network on a single machine using Mininet~\cite{Lantz2010}.
We use Open vSwitch~\cite{Pfaff2009} as our switch which supports queues with varying bandwidth guarantees.
Queuing is performed by the hierarchical token bucket queuing discipline in the Linux kernel.
We simply specify a set of queues for each switch port with varying minimum bandwidth guarantees.
Our controller is written in Python using the POX~\cite{Gude2008} platform and OpenFlow~\cite{McKeown2008} 1.0.
